Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-09-03 document/main.tex
Progress

% === All of the Packages I use frequently ===
\usepackage{../packages/shared}

@@

% === Numbering For amsthm theorem environments ===
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

@@

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yright}}
\newcommand{\res}{\mathrel{\Yleft}}
\newcommand{\gelem}{\varphi}
\newcommand{\action}[1]{\gelem\bs{#1}}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\setoperator{Out} % Outcome space
\setoperator{Dom} % Domian

@@

    \begin{definition}
        This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
        % Where the valuation product between outcome spaces is defined as follows,\footnote{At this level, a valuation product behaves analogously to a Cartesian product. However in \cref{def:extendable_set}, we define the a valuation product between outcomes and outcomes spaces.}
        \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
        As a natural generalization, when considering a larger set of random variables $V = \bc{v_i}_{i \in \bs{k}}$ we define the joint outcome space in an analogous way,
        \[ \Out{V} \defined \bc{f: \bc{v_i}_{i \in \bs{k}} \to \bc{O_{v_i}}_{i \in \bs{k}} \mid \forall i \in \bs{k} : f\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
        Each outcome $f$ can be compactly represented as a set of mappings over each element of $V$.
        \[ f = \bc{v_1 \mapsto f\br{v_1}, \ldots, v_k \mapsto f\br{v_k}} = \bc{v_i\mapsto f\br{v_i}}_{i \in \bs{k}} \]
        The domain of $f$ refers to the set of random variables it valuates and is denoted as $\Dom{f}$. If $f \in \Out{V}$, then $\Dom{f} = V$.
        % Where the joint outcome labels are elements of a Cartesian product,
        % \[ O_V \defined O_{v_1} \times \cdots \times O_{v_{\abs{V}}}  \]

@@

    \begin{remark}
        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if they are extendable to some outcome $f \in \Out{V \cup W}$.
        \[ g \com h \iff \exists f \in \Out{V \cup W} \mid g \ext f \res h \]
        In fact, such an $f$ is uniquely defined,
        \[ \forall v \in V : f\br{v} = \begin{cases}
            g\br{v} & v \in V \\
            h\br{v} & v \in W
        \end{cases} \]
    \end{remark}

@@

@@

    \section{Triangle Scenario}
    \todo[TC]{Discuss the Triangle Scenario, previous work done on it, etc.}

    Figure 8 of Appendix E \cite{Henson_2014}
    Figure 1 of \cite{Inflation}

    Focusing on the inflation depicted in \cref{fig:inflated_triangle_scenario}, we obtained the maximally pre-injectable sets through the procedure outlined in \cite{Inflation}.
    \begin{equation*}
        \eq \label{eq:pre-injectable_triangle_scenario}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    As can be counted, there are $12$ maximally pre-injectable sets which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$)

    \begin{figure}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../figures/causal_structures/triangle_scenario}}
            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
            \label{fig:triangle_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{0.8}{\input{../figures/causal_structures/inflated_triangle_scenario}}
            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
            \label{fig:inflated_triangle_scenario}
        \end{minipage}
    \end{center}
    \end{figure}

@@

        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$. Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.
    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?}
    \todo[TC]{Connection between contextuality and Compatibility via the marginal problem for causal parameters}
    \todo[TC]{Discuss what is meant by a `complete' solution to the marginal problem}
    \todo[TC]{Maybe define the possibilistic marginal problem for later}

@@

    In this work, we obtain inequalities that constrain the set of injectable marginal models $\bc{\prob[N'] \mid N' \in \ImInj[\graph]{\graph'}}$ for the inflated Triangle Scenario of \cref{fig:triangle_scenario} by considering the marginal problem (see \cref{sec:comp_con_mp}) for the set of \term{maximally pre-injectable sets}\footnote{The set of all pre-injectable sets forms a topological \textit{simplicial conplex}. `Maximal' refers to the pre-injectable sets that are no proper subset of another.}. As defined by \cite{Inflation}, a pre-injectable set $V$ is a subset of $\nodes'$ that can be written as the decomposed into the union of injectable sets $V = \bigcup_i N'_i$ where $\bc{N'_i \in \Inj[\graph]{\graph'}}$ that are mutually \term{ancestrally independent},
    \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions \cite{Pearl_2009},
    \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
    This turns linear inequalities over the pre-injectable distributions into polynomial inequalities over the injectable distributions, allowing one to replace all such distributions with equivalent distributions over the original random variables of $\nodes$. $\PreInj[\graph]{\graph'}$ will denote the set of all pre-injectable sets.

>>>>

\usepackage{silence}
\WarningFilter{revtex4-1}{Repair the float}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
% === All of the Packages I use frequently ===
\usepackage{../packages/shared}

@@

% === Numbering For amsthm theorem environments ===
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

@@

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gelem}{\varphi}
\newcommand{\action}[1]{\gelem\bs{#1}}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mext}[1]{E_{#1}}
\newcommand{\mul}[1]{\Gamma_{#1}}
\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
\newcommand{\ts}{\mathcal{T}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\setoperator{Out} % Outcome space
\setoperator{Dom} % Domian

@@

    \begin{definition}
        % This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
        % Where the valuation product between outcome spaces is defined as follows,\footnote{At this level, a valuation product behaves analogously to a Cartesian product. However in \cref{def:extendable_set}, we define the a valuation product between outcomes and outcomes spaces.}
        % \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
        As a natural generalization, when considering a larger set of random variables $V = \bc{v_i}_{i \in \bs{k}}$ we define the joint outcome space in an analogous way,
        \[ \Out{V} \defined \bc{f: \bc{v_i}_{i \in \bs{k}} \to \bc{O_{v_i}}_{i \in \bs{k}} \mid \forall i \in \bs{k} : f\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
        Each outcome $f$ can be compactly represented as a set of mappings over each element of $V$.
        \[ f = \bc{v_1 \mapsto f\br{v_1}, \ldots, v_k \mapsto f\br{v_k}} = \bc{v_i\mapsto f\br{v_i}}_{i \in \bs{k}} \]
        The domain of $f$ refers to the set of random variables it valuates and is denoted as $\Dom{f}$. If $f \in \Out{V}$, then $\Dom{f} = V$.
        % Where the joint outcome labels are elements of a Cartesian product,
        % \[ O_V \defined O_{v_1} \times \cdots \times O_{v_{\abs{V}}}  \]

@@

    \begin{remark}
        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if extensions of some outcome $f \in \Out{V \cap W}$.
        \[ g \com h \iff \exists f \in \Out{V \cap W} \mid g \res f \ext h \]
        In fact, such an $f$ is uniquely defined,
        \[ \forall v \in V \cap W : f\br{v} = g\br{v} = g\br{v} \]
    \end{remark}

@@

    \subsection{Preliminary Definitions}

    Before discussing the present work, we

@@

@@

    \begin{definition}
        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$. Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.
    \end{definition}

    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?}
    \todo[TC]{Connection between contextuality and Compatibility via the marginal problem for causal parameters}
    \todo[TC]{Discuss what is meant by a `complete' solution to the marginal problem}
    \todo[TC]{Maybe define the possibilistic marginal problem for later}

    \section{The Triangle Scenario}
    \label{sec:triangle_scenario}
    \begin{figure}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../figures/causal_structures/triangle_scenario}}
            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
            \label{fig:triangle_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{0.8}{\input{../figures/causal_structures/inflated_triangle_scenario}}
            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
            \label{fig:inflated_triangle_scenario}
        \end{minipage}
    \end{center}
    \end{figure}

    The triangle scenario $\ts$ is a causal structure composed of $3$ parties $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$. It has that has been studied extensively in existing literature (see \cite[Fig. 1]{Steudel_2010}, \cite[Fig. 6]{Chaves_2014}, \cite[Fig. 8]{Branciard_2012}, \cite[Fig. 8, Appendix E]{Henson_2014}, \cite[Fig. 3]{Fritz_2012}, \cite[Fig. 1]{Inflation}, $\ldots$) and is reproduced here in \cref{fig:triangle_scenario} for convenience. At the time of publication for \cite{Branciard_2012} it was noted that characterizing locality in $\ts$ remained an open problem and that identifying locality constraints in this configuration seemed challenging. In \cite{Henson_2014}, $\ts$ was classified as an ``interesting'' causal structure.\footnote{Indicating that conditional independence relations are not a sufficient characterization of compatibility for $\ts$ \cite{Henson_2014}. Note that in $\ts$ there are \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Additionally $\ts$ is presented along with a family of entropic inequalities that constrain the set of compatible distributions \cite{Henson_2014}. Furthermore in \cite{Fritz_2012}, Fritz demonstrated that $\ts$ is the \textit{smallest} correlation scenario in which their exists quantum incompatible distributions by explicitly mentioning one (which we elect to call the \textit{Fritz distribution} in \cref{sec:fritz_dist}) and poses an important question asking if other incompatible quantum distributions exist. Finally in \cite{Inflation}, Wolfe et. al. make use of $\ts$ along with the Bell Scenario to demonstrate a novel technique for causal inference called the \textit{inflation technique} (summarized in \cref{sec:summary_inflation}). Wolfe et. al. validate the power and applicability of the inflation technique by proving incompatibility between $\ts$ and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints \cite{Inflation}. Moreover, a family of polynomial, $2$-outcome, compatibility inequalities are explicitly derived for an exemplary inflation of $\ts$ and $37$ non-trivial representatives are printed in \cite{Inflation}.

    Identifying quantum-accessible distributions that are incompatible with the triangle scenario is of particular importance as it \todo[TC]{Discuss why we are doing this.}

    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit states and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in \cite{Inflation} as well as the entropic inequalities presented by \cite{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-locality is not present in $\ts$ for \textit{two-outcome} measurements. We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in $\ts$ for a larger number of outcomes.

    Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}. We develop a new technique which we call the \textit{extendable covering procedure (ECP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes. We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution. Before discussing the ECP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of \cite{Inflation}. Following these summaries of existing work, we present the ECP and its connection to Hardy-type paradoxes \cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities \cite{Abramsky_2011}. Moreover, the ECP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models. To conclude, we subject our found inequalities to non-linear optimizations and discuss the implications of our results.

    \section{The Fritz Distribution}
    \label{sec:fritz_dist}
    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario \cite{Fritz_2012}. Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
    \begin{align*}
    \eq \label{eq:fritz_dist}
    \begin{split}
    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
    \end{split}
    \end{align*}
    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
    \begin{equation}
    \begin{gathered}
    \label{eq:fritz_quantum_realization}
    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+} \\
    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gathered}
    \end{equation}
    Where for convenience of notation $\psi_x$ is used to denote the superposition,
    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.

    Fritz first proved it's incompatibility \cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario. In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality. To illustrate this, begin with the CHSH inequality \cite{CHSH_Original},
    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively. Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
    \begin{gather*}
    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
    \end{gather*}
    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$ \cite{Cirelson_1980}.

    In \cite{Fritz_2012}, Fritz posits the following question: \textit{Find an example of non-classical quantum correlations in $\ts$ together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}

    \todo[TC]{Summarize Problem 2.17 in fritz BBT, make it more formal}

@@

    In this work, we obtain inequalities that constrain the set of injectable marginal models $\bc{\prob[N'] \mid N' \in \ImInj[\graph]{\graph'}}$ for the inflated Triangle Scenario of \cref{fig:triangle_scenario} by considering the marginal problem (see \cref{sec:comp_con_mp}) for the set of \term{maximally pre-injectable sets}\footnote{The set of all pre-injectable sets forms a topological \textit{simplicial conplex}. `Maximal' refers to the pre-injectable sets that are no proper subset of another.}. A pre-injectable set $V$ is a subset of $\nodes'$ that can be decomposed into the disjoint union of injectable sets $V = \coprod_i N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ that are mutually \term{ancestrally independent},
    \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions \cite{Pearl_2009},
    \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
    This turns linear inequalities over the pre-injectable distributions into polynomial inequalities over the injectable distributions, allowing one to replace all such distributions with equivalent distributions over the original random variables of $\nodes$. $\PreInj[\graph]{\graph'}$ will denote the set of all pre-injectable sets.

    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in \cite{Inflation}.
    \begin{equation*}
        \eq \label{eq:pre-injectable_triangle_scenario}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    As can be counted, there are $12$ maximally pre-injectable sets $\ts'$ which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$). The maximally pre-injectable sets $\bc{V_i}_{i \in \bs{12}}$ form a maximal marginal scenario $\mscenario$ over the observable nodes of $\ts'$ when equipped with outcome labels. Using \cref{lem:inflation} inequalities $\mathcal{I}_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $\mathcal{I}_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
    \[ \ImInj[\ts]{\ts'} = \bc{\bc{A, B, C}, \bc{A}, \bc{B}, \bc{C}} \]

    \section{Certificate Inequalities}
    \label{sec:certificate_inequalities}
    \subsection{Casting the Marginal Problem as a Linear Program}
    After obtaining the maximal pre-injectable sets associated with a particular inflation, one can write the marginal problem of \cref{def:marginal_problem} as a linear program. The key observation is that marginalization is a \textit{linear} operator that can be performed via a matrix multiplication. To do this, we will define the \textit{incidence matrix}.
    \begin{definition}
        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} outcomes $j \in \Out{\jointvar}$ and the rows are indexed by \textit{marginal} outcomes $m \in \Out{\mscenario}$. The entries of $M$ are populated whenever a row index is extendable to a column index.
        \[ M\bs{m, j} = \de_{m \ext j} \defined \begin{cases}
            1 & m \ext j \\
            0 & \text{otherwise}
        \end{cases} \]
        Where $\de_{m \ext j}$ is an \textit{extendability indicator}. The incidence matrix has $\abs{\Out{\jointvar}}$ columns and $\abs{\Out{\mscenario}} = \sum_{i\in \bs{k}} \abs{\Out{V_i}}$ rows. The number of non-zero entries of $M$ is a simple expression,
        \[ \sum_{i\in\bs{k}} \abs{\Out{V_i}}\abs{\Out{\jointvar \setminus V_i}} = \sum_{i\in \bs{k}} \abs{\Out{\jointvar}} = k\abs{\Out{\jointvar}} \]
        This is due to the fact that each marginal context contributes a single non-zero entry to each column of $M$, resulting in $k\abs{\Out{\jointvar}}$ total non-zero entries.
    \end{definition}
    \todo[TC]{Computationally Efficient generation?}

    To illustrate this concretely, consider the following example:
    \begin{example}
        \label{ex:marginal_matrix}
        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and consider the marginal scenario $\mscenario = \bc{\bc{a,c}, \bc{b}}$. The incidence matrix becomes:
        \[ M = \kbordermatrix{
            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
            (a\mapsto0, c\mapsto0) & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
            (a\mapsto0, c\mapsto1) & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 \\
            (a\mapsto1, c\mapsto0) & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 \\
            (a\mapsto1, c\mapsto1) & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
            (b\mapsto0)            & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
            (b\mapsto1)            & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1
        } \]
    \end{example}

    \begin{example}
        The marginal problem for the inflated causal structure $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\ts]{\ts'} = \bc{V_1, \ldots, V_{12}}$. Equipping the observed nodes of $\ts'$ with $4$-element outcome labels, the incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
        \begin{align*}
            &\text{\# Rows} = \abs{\Out{\mscenario}} = \sum_{i=1}^{12} \abs{\Out{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
            &\text{\# Columns} = \abs{\Out{\jointvar}} = 4^{\abs{\jointvar}} = 4^{12} = 16,777,216
        \end{align*}
        With $12 \cdot 4^{12} = 201,326,592$ non-zero entries. For obvious reasons, no attempt is made to reproduce it here.
    \end{example}

    In order to describe how marginalization can be written as matrix multiplication $M \cdot x = b$, two more quantities need to be described:
